Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-10 paper/Draft.tex
Generate Revision efficiency test for Indididual SCE. Using 10-month-apart 2-year forecast and 1-year forecast.
Include revision efficiency tests for SCE using population revisions from 2-year to 1-year. Need to change the texts.

					\begin{tabular}{lllllllll}

@@

						& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\

@@

						\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\

@@

						& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\

@@

						L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
						&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
						L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
						&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
						L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
						&               &           &          & (0.048)  &               &           &           & (0.069)   \\
						SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
						&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
						SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
						&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
						& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
						Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\

@@

						N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
						$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\

@@

						\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\

@@

						L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
						&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
						L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
						&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
						L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
						&               &           &          & (0.121)  &               &           &           & (0.149)   \\
						Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
						& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\

@@

						N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
						$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\

>>>>

				\begin{tabular}{llllllllllllll}

@@

					& SPF CPI       &           &          &          & SPF PCE       &           &           &           & \multicolumn{5}{l}{SCE}                                              \\

@@

					\multicolumn{14}{l}{Test 1.  Revision efficiency of mean forecast}                                                                                                                               \\

@@

					& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                     & Mean revision & t-1      & t-1- t-2 & t-1-t-3  \\

@@

					L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  & L.InfExp\_Mean\_rv  &               & 0.884*** & 0.750*** & 0.685**  \\
					&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   &                     &               & (0.084)  & (0.171)  & (0.211)  \\
					L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  & L2.InfExp\_Mean\_rv &               &          & 0.206    & 0.199    \\
					&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   &                     &               &          & (0.173)  & (0.185)  \\
					L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     & L3.InfExp\_Mean\_rv &               &          & -0.073   & -0.122   \\
					&               &           &          & (0.048)  &               &           &           & (0.069)   &                     &               &          & (0.191)  & (0.264)  \\
					SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           & L4.InfExp\_Mean\_rv &               &          &          & 0.055    \\
					&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           &                     &               &          &          & (0.217)  \\
					SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** & L5.InfExp\_Mean\_rv &               &          &          & 0.073    \\
					&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   &                     &               &          &          & (0.242)  \\
					&               &           &          &          &               &           &           &           & L6.InfExp\_Mean\_rv &               &          &          & -0.016   \\
					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.140)  \\
					Constant               & -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   & Constant               & -0.263***     & -0.016   & -0.010   & -0.005   \\
					& (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   &                     & (0.038)       & (0.029)  & (0.033)  & (0.042)  \\

@@

					N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       & N                   & 41            & 40       & 38       & 35       \\
					$R^2$               & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     & $R^2$               & 0.000         & 0.717    & 0.732    & 0.690    \\

@@

					\multicolumn{14}{l}{Test 2. Revision efficiency of uncertainty}             \\

@@

					L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    & L.InfExp\_Var\_rv   &               & 0.731*** & 0.723*** & 0.785*** \\
					&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   &                     &               & (0.108)  & (0.159)  & (0.161)  \\
					L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    & L2.InfExp\_Var\_rv  &               &          & 0.283    & 0.174    \\
					&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   &                     &               &          & (0.197)  & (0.246)  \\
					L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    & L3.InfExp\_Var\_rv  &               &          & -0.336   & -0.410   \\
					&               &           &          & (0.121)  &               &           &           & (0.149)   &                     &               &          & (0.186)  & (0.266)  \\
					&               &           &          &          &               &           &           &           & L4.InfExp\_Var\_rv  &               &          &          & 0.270    \\
					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.219)  \\
					&               &           &          &          &               &           &           &           & L5.InfExp\_Var\_rv  &               &          &          & -0.065   \\
					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.248)  \\
					&               &           &          &          &               &           &           &           & L6.InfExp\_Var\_rv  &               &          &          & -0.082   \\
					&               &           &          &          &               &           &           &           &                     &               &          &          & (0.172)  \\
					Constant               & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   & Constant               & -0.590**      & -0.186   & -0.199   & -0.163   \\
					& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   &                     & (0.174)       & (0.155)  & (0.164)  & (0.171)  \\

@@

					N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       & N                   & 41            & 40       & 38       & 35       \\
					$R^2$               & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723     & $R^2$               & 0.000         & 0.549    & 0.597    & 0.619 \\
